The Precambrian paleogeography of Laurentia

### 2020-09-17 Manuscript/pole_table_edited.tex
uniform spelling of dike

@@

      Laurentia-Superior(East) &                     Otto Stock dykes and aureole &      B &     279.9 &      48.0 & 227.0 &  69.0 &       4.8 &     2676$^{+5}_{-5}$ &                               \cite{Pullaiah1975b} \\ \hline

@@

      Laurentia-Superior(East) &                       Ptarmigan-Mistassini dykes &      B &     287.0 &      54.0 & 213.0 & -45.3 &      13.8 &     2505$^{+2}_{-2}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(East) &                               Matachewan dykes R &      A &     278.0 &      48.0 & 238.3 & -44.1 &       1.6 &   2466$^{+23}_{-23}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(East) &                               Matachewan dykes N &      A &     278.0 &      48.0 & 239.5 & -52.3 &       2.4 &     2446$^{+3}_{-3}$ &                                  \cite{Evans2010a} \\ \hline
               Laurentia-Slave &                                     Malley dykes &      A &     249.8 &      64.2 & 310.0 & -50.8 &       6.7 &     2231$^{+2}_{-2}$ &                                 \cite{Buchan2012a} \\ \hline
      Laurentia-Superior(East) &                                 Senneterre dykes &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218$^{+6}_{-6}$ &                                 \cite{Buchan1993a} \\ \hline

@@

               Laurentia-Slave &                                     Dogrib dykes &      A &     245.5 &      62.5 & 315.0 & -31.0 &       7.0 &     2193$^{+2}_{-2}$ &                               \cite{Mitchell2014a} \\ \hline
      Laurentia-Superior(East) &                                Biscotasing dykes &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170$^{+3}_{-3}$ &                                  \cite{Evans2010a} \\ \hline
             Laurentia-Wyoming &  Rabbit Creek, Powder River and South Path Dykes &      A &     252.8 &      43.9 & 339.2 &  65.5 &       7.6 &    2160$^{+11}_{-8}$ &                                 \cite{Kilian2015a} \\ \hline
               Laurentia-Slave &                                      Indin dykes &      A &     245.6 &      62.5 & 256.0 & -36.0 &       7.0 &    2126$^{+3}_{-18}$ &                                 \cite{Buchan2016a} \\ \hline
      Laurentia-Superior(West) &                                 Marathon dykes N &      A &     275.0 &      49.0 & 198.2 &  45.4 &       7.7 &     2124$^{+3}_{-3}$ &                                  \cite{Halls2008a} \\ \hline
      Laurentia-Superior(West) &                                 Marathon dykes R &      A &     275.0 &      49.0 & 182.2 &  55.1 &       7.5 &     2104$^{+3}_{-3}$ &                                  \cite{Halls2008a} \\ \hline
      Laurentia-Superior(West) &                               Cauchon Lake dykes &      A &     263.0 &      56.0 & 180.9 &  53.8 &       7.7 &     2091$^{+2}_{-2}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(West) &                               Fort Frances dykes &      A &     266.0 &      48.0 & 184.6 &  42.8 &       6.1 &     2077$^{+5}_{-5}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(East) &                                 Lac Esprit dykes &      A &     282.0 &      53.0 & 170.5 &  62.0 &       6.4 &     2069$^{+1}_{-1}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Greenland-Nain &                                  Kangamiut Dykes &      B &     307.0 &      66.0 & 273.8 &  17.1 &       2.7 &   2042$^{+12}_{-12}$ &                                 \cite{Fahrig1976b} \\ \hline
               Laurentia-Slave &                                Lac de Gras dykes &      A &     249.6 &      64.4 & 267.9 &  11.8 &       7.1 &     2026$^{+5}_{-5}$ &                                 \cite{Buchan2009a} \\ \hline
      Laurentia-Superior(East) &                                      Minto dykes &      A &     285.0 &      57.0 & 171.5 &  38.7 &      13.1 &     1998$^{+2}_{-2}$ &                                  \cite{Evans2010a} \\ \hline

@@

      Laurentia-Superior(West) &                              Molson (B+C2) dykes &      A &     262.0 &      55.0 & 218.0 &  28.9 &       3.8 &     1879$^{+6}_{-6}$ &                                  \cite{Evans2010a} \\ \hline

@@

                 Laurentia-Rae &                                    Sparrow Dykes &      B &     250.2 &      61.6 & 291.0 &  12.0 &       7.9 &     1827$^{+4}_{-4}$ &                                \cite{McGlynn1974a} \\ \hline

@@

                     Laurentia &                                    Cleaver Dykes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741$^{+5}_{-5}$ &                                  \cite{Irving2004a} \\ \hline
           Laurentia-Greenland &                      Melville Bugt diabase dykes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633$^{+5}_{-5}$ &                                  \cite{Halls2011a} \\ \hline

@@

                     Laurentia &                               Tobacco Root dykes &      B &     247.6 &      47.4 & 216.1 &   8.7 &      10.5 &   1448$^{+49}_{-49}$ &                                 \cite{Harlan2008a} \\ \hline

@@

           Laurentia-Greenland &                    Victoria Fjord dolerite dykes &      B &     315.3 &      81.5 & 231.7 &  10.3 &       4.3 &     1382$^{+2}_{-2}$ &                             \cite{Abrahamsen1987a} \\ \hline

@@

           Laurentia-Greenland &                                Kungnat Ring Dyke &      B &     311.7 &      61.2 & 198.7 &   3.4 &       3.2 &     1275$^{+2}_{-2}$ &                                  \cite{Piper1977b} \\ \hline
                     Laurentia &                       Mackenzie dykes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267$^{+2}_{-2}$ &                                 \cite{Buchan2000a} \\ \hline
           Laurentia-Greenland &                       West Gardar Dolerite Dykes &      B &     311.7 &      61.2 & 201.7 &   8.7 &       6.6 &     1244$^{+8}_{-8}$ &                                  \cite{Piper1977b} \\ \hline
           Laurentia-Greenland &                    West Gardar Lamprophyre Dykes &      B &     311.7 &      61.2 & 206.4 &   3.2 &       7.2 &   1238$^{+11}_{-11}$ &                                  \cite{Piper1977b} \\ \hline
                     Laurentia &                           Sudbury Dykes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237$^{+5}_{-5}$ &                                 \cite{Palmer1977a} \\ \hline

@@

           Laurentia-Greenland &                               Hviddal Giant Dyke &      B &     313.7 &      60.9 & 215.3 &  33.2 &       9.6 &     1184$^{+5}_{-5}$ &                                  \cite{Piper1977a} \\ \hline

@@

           Laurentia-Greenland &                               Giant Gabbro Dykes &      B &     313.7 &      60.9 & 226.1 &  42.3 &       9.4 &     1163$^{+2}_{-2}$ &                                  \cite{Piper1977a} \\ \hline
           Laurentia-Greenland &                             NE-SW Trending dykes &      B &     314.6 &      61.1 & 230.8 &  33.4 &       5.7 &     1160$^{+5}_{-5}$ &                                  \cite{Piper1992a} \\ \hline
                     Laurentia &                        Ontario lamprophyre dykes &      NR &     273.3 &      48.8 & 223.3 &  58.0 &       9.2 &   1143$^{+10}_{-10}$ &                                 \cite{Piispa2018a} \\ \hline
                     Laurentia &                                    Abitibi Dykes &      A &     279.0 &      48.0 & 215.5 &  48.8 &      14.1 &     1141$^{+2}_{-2}$ &                                  \cite{Ernst1993a} \\ \hline

@@

            Laurentia &                                  Gunbarrel dykes &      B &     248.7 &      44.8 & 138.2 &   9.1 &      12.0 &      778$^{+2}_{-2}$ &  Calculation from \cite{Eyster2019a} based on data of \cite{Harlan1993a, Harlan1997a}  \\ \hline

@@

                     Laurentia &                                 Long Range Dykes &      B &     303.3 &      53.7 & 175.3 & -19.0 &      17.4 &      615$^{+2}_{-2}$ &                                 \cite{Murthy1992a} \\ \hline

>>>>

%make dike throughout for consistency

@@

      Laurentia-Superior(East) &                     Otto Stock dikes and aureole &      B &     279.9 &      48.0 & 227.0 &  69.0 &       4.8 &     2676$^{+5}_{-5}$ &                               \cite{Pullaiah1975b} \\ \hline

@@

      Laurentia-Superior(East) &                       Ptarmigan-Mistassini dikes &      B &     287.0 &      54.0 & 213.0 & -45.3 &      13.8 &     2505$^{+2}_{-2}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(East) &                               Matachewan dikes R &      A &     278.0 &      48.0 & 238.3 & -44.1 &       1.6 &   2466$^{+23}_{-23}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(East) &                               Matachewan dikes N &      A &     278.0 &      48.0 & 239.5 & -52.3 &       2.4 &     2446$^{+3}_{-3}$ &                                  \cite{Evans2010a} \\ \hline
               Laurentia-Slave &                                     Malley dikes &      A &     249.8 &      64.2 & 310.0 & -50.8 &       6.7 &     2231$^{+2}_{-2}$ &                                 \cite{Buchan2012a} \\ \hline
      Laurentia-Superior(East) &                                 Senneterre dikes &      A &     283.0 &      49.0 & 284.3 & -15.3 &       5.5 &     2218$^{+6}_{-6}$ &                                 \cite{Buchan1993a} \\ \hline

@@

               Laurentia-Slave &                                     Dogrib dikes &      A &     245.5 &      62.5 & 315.0 & -31.0 &       7.0 &     2193$^{+2}_{-2}$ &                               \cite{Mitchell2014a} \\ \hline
      Laurentia-Superior(East) &                                Biscotasing dikes &      A &     280.0 &      48.0 & 223.9 &  26.0 &       7.0 &     2170$^{+3}_{-3}$ &                                  \cite{Evans2010a} \\ \hline
             Laurentia-Wyoming &  Rabbit Creek, Powder River and South Path dikes &      A &     252.8 &      43.9 & 339.2 &  65.5 &       7.6 &    2160$^{+11}_{-8}$ &                                 \cite{Kilian2015a} \\ \hline
               Laurentia-Slave &                                      Indin dikes &      A &     245.6 &      62.5 & 256.0 & -36.0 &       7.0 &    2126$^{+3}_{-18}$ &                                 \cite{Buchan2016a} \\ \hline
      Laurentia-Superior(West) &                                 Marathon dikes N &      A &     275.0 &      49.0 & 198.2 &  45.4 &       7.7 &     2124$^{+3}_{-3}$ &                                  \cite{Halls2008a} \\ \hline
      Laurentia-Superior(West) &                                 Marathon dikes R &      A &     275.0 &      49.0 & 182.2 &  55.1 &       7.5 &     2104$^{+3}_{-3}$ &                                  \cite{Halls2008a} \\ \hline
      Laurentia-Superior(West) &                               Cauchon Lake dikes &      A &     263.0 &      56.0 & 180.9 &  53.8 &       7.7 &     2091$^{+2}_{-2}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(West) &                               Fort Frances dikes &      A &     266.0 &      48.0 & 184.6 &  42.8 &       6.1 &     2077$^{+5}_{-5}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Superior(East) &                                 Lac Esprit dikes &      A &     282.0 &      53.0 & 170.5 &  62.0 &       6.4 &     2069$^{+1}_{-1}$ &                                  \cite{Evans2010a} \\ \hline
      Laurentia-Greenland-Nain &                                  Kangamiut dikes &      B &     307.0 &      66.0 & 273.8 &  17.1 &       2.7 &   2042$^{+12}_{-12}$ &                                 \cite{Fahrig1976b} \\ \hline
               Laurentia-Slave &                                Lac de Gras dikes &      A &     249.6 &      64.4 & 267.9 &  11.8 &       7.1 &     2026$^{+5}_{-5}$ &                                 \cite{Buchan2009a} \\ \hline
      Laurentia-Superior(East) &                                      Minto dikes &      A &     285.0 &      57.0 & 171.5 &  38.7 &      13.1 &     1998$^{+2}_{-2}$ &                                  \cite{Evans2010a} \\ \hline

@@

      Laurentia-Superior(West) &                              Molson (B+C2) dikes &      A &     262.0 &      55.0 & 218.0 &  28.9 &       3.8 &     1879$^{+6}_{-6}$ &                                  \cite{Evans2010a} \\ \hline

@@

                 Laurentia-Rae &                                    Sparrow dikes &      B &     250.2 &      61.6 & 291.0 &  12.0 &       7.9 &     1827$^{+4}_{-4}$ &                                \cite{McGlynn1974a} \\ \hline

@@

                     Laurentia &                                    Cleaver dikes &      A &     242.0 &      67.5 & 276.7 &  19.4 &       6.1 &     1741$^{+5}_{-5}$ &                                  \cite{Irving2004a} \\ \hline
           Laurentia-Greenland &                      Melville Bugt diabase dikes &      B &     303.0 &      74.6 & 273.8 &   5.0 &       8.7 &     1633$^{+5}_{-5}$ &                                  \cite{Halls2011a} \\ \hline

@@

                     Laurentia &                               Tobacco Root dikes &      B &     247.6 &      47.4 & 216.1 &   8.7 &      10.5 &   1448$^{+49}_{-49}$ &                                 \cite{Harlan2008a} \\ \hline

@@

           Laurentia-Greenland &                    Victoria Fjord dolerite dikes &      B &     315.3 &      81.5 & 231.7 &  10.3 &       4.3 &     1382$^{+2}_{-2}$ &                             \cite{Abrahamsen1987a} \\ \hline

@@

           Laurentia-Greenland &                                Kungnat Ring dike &      B &     311.7 &      61.2 & 198.7 &   3.4 &       3.2 &     1275$^{+2}_{-2}$ &                                  \cite{Piper1977b} \\ \hline
                     Laurentia &                       Mackenzie dikes grand mean &      A &     250.0 &      65.0 & 190.0 &   4.0 &       5.0 &     1267$^{+2}_{-2}$ &                                 \cite{Buchan2000a} \\ \hline
           Laurentia-Greenland &                       West Gardar Dolerite dikes &      B &     311.7 &      61.2 & 201.7 &   8.7 &       6.6 &     1244$^{+8}_{-8}$ &                                  \cite{Piper1977b} \\ \hline
           Laurentia-Greenland &                    West Gardar Lamprophyre dikes &      B &     311.7 &      61.2 & 206.4 &   3.2 &       7.2 &   1238$^{+11}_{-11}$ &                                  \cite{Piper1977b} \\ \hline
                     Laurentia &                           Sudbury dikes Combined &      A &     278.6 &      46.3 & 192.8 &  -2.5 &       2.5 &     1237$^{+5}_{-5}$ &                                 \cite{Palmer1977a} \\ \hline

@@

           Laurentia-Greenland &                               Hviddal Giant dike &      B &     313.7 &      60.9 & 215.3 &  33.2 &       9.6 &     1184$^{+5}_{-5}$ &                                  \cite{Piper1977a} \\ \hline

@@

           Laurentia-Greenland &                               Giant Gabbro dikes &      B &     313.7 &      60.9 & 226.1 &  42.3 &       9.4 &     1163$^{+2}_{-2}$ &                                  \cite{Piper1977a} \\ \hline
           Laurentia-Greenland &                             NE-SW Trending dikes &      B &     314.6 &      61.1 & 230.8 &  33.4 &       5.7 &     1160$^{+5}_{-5}$ &                                  \cite{Piper1992a} \\ \hline
                     Laurentia &                        Ontario lamprophyre dikes &      NR &     273.3 &      48.8 & 223.3 &  58.0 &       9.2 &   1143$^{+10}_{-10}$ &                                 \cite{Piispa2018a} \\ \hline
                     Laurentia &                                    Abitibi dikes &      A &     279.0 &      48.0 & 215.5 &  48.8 &      14.1 &     1141$^{+2}_{-2}$ &                                  \cite{Ernst1993a} \\ \hline

@@

            Laurentia &                                  Gunbarrel dikes &      B &     248.7 &      44.8 & 138.2 &   9.1 &      12.0 &      778$^{+2}_{-2}$ &  Calculation from \cite{Eyster2019a} based on data of \cite{Harlan1993a, Harlan1997a}  \\ \hline

@@

                     Laurentia &                                 Long Range dikes &      B &     303.3 &      53.7 & 175.3 & -19.0 &      17.4 &      615$^{+2}_{-2}$ &                                 \cite{Murthy1992a} \\ \hline
